troubleshooting

### 2024-09-26 README.Rmd
passed Rcmd check
rcmd check pass

[![R-CMD-check](https://github.com/baynec2/mspms/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/baynec2/mspms/actions/workflows/R-CMD-check.yaml)
[![Codecov test
coverage](https://codecov.io/gh/baynec2/mspms/branch/main/graph/badge.svg)](https://app.codecov.io/gh/baynec2/mspms?branch=bioconductor)

@@

```{r}
processed_qf <- process_qf(peaks_prepared_data)
processed_qf
```

>>>>

[![R-CMD-check](https://github.com/baynec2/mspms/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/baynec2/mspms/actions/workflows/R-CMD-check.yaml)
[![Codecov test
coverage](https://codecov.io/gh/baynec2/mspms/branch/main/graph/badge.svg)](https://app.codecov.io/gh/baynec2/mspms?branch=main)

@@

```{r}
set.seed(2)
processed_qf <- process_qf(peaks_prepared_data)
processed_qf
```
